---
title: "碳排放管理對於企業股價之影響"
author: "Names _____"
date: "5/17/2022"
output: html_document
---
<style>
    body { background-color: #A9CAAB; }
    pre, pre:not([class]) { background-color: gainsboro; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(readxl)
library(caret)
library(tidyverse)
library(rpart)
library(rpart.plot)
library(rsample) 
library(randomForest)
library(modelr)
library(corrplot)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(DT)
library(glmnet)

# read in the file, only usign esg_df (the larger set)
esg_df<- read_excel("data/ACWI-ESG-Results_1.xlsx")
esg_uni_df <-read_excel("data/ACWI-ESG-Universal-Results_1.xlsx")

# override the default setting of ggplot
theme_set(theme_minimal())
```

## 研究方法

利用MSCI ACWI Europe ESG Leaders Index 中的個股與其碳排管理指標，進行單因子迴歸分析，以探討「碳排管理是否能帶來超額報酬」之課題。由於產業間業務性質差異甚大，因此也會將個股按照產業區分，以達到產業中立之目的。

## 研究動機

分析師報告中證實MSCI ACWI ESG Leaders Index的確在2020年疫情爆發之後較MSCI ACWI Index取得相對好的報酬。近期歐盟祭出2050年碳中和目標與一系列政策，企業因此面臨低碳轉型風險，因此我們希望將樣本池鎖定歐盟企業，且著重於ESG中的碳排放管理指標，期許能夠針對這個課題得出一些新發現。


### data cleaning - explain
since carbon emission is our focus, and all the industries tend to have drastic different in their carbon emission amount, we seperate our companies into three industries: carbon heavy industry, carbon light industry, and energy industry.  
```{r data cleaning, echo=FALSE, warning=FALSE}
# only using EU countries
esg_eu_df = esg_df %>% filter(ISSUER_CNTRY_DOMICILE %in% c("AT", "BE", "BG", "HR", "CY", "DK", "EE", "FI", "FR", "DE", "GR", "HU", "IE", "IT", "LV", "LT", "LU", "MT", "NL", "PL","PT","RO", "SK", "SI", "ES", "SE"))

# seperate into carb heavt/light and ENERGY data frames
carb_heavy_df = esg_df %>% filter(Industry %in% c("Materials", "Utilities", "Industrial"))
carb_light_df = esg_df %>% 
  filter(!Industry %in% c("Materials", "Utilities", "Energy", "Industrial")) 
energy_df = esg_df %>% filter(Industry %in% c("Energy"))

# chnange "return" variables from character to double
carb_heavy_df[, c(31:33)] <- sapply(carb_heavy_df[, c(31:33)], as.numeric)
carb_light_df[, c(31:33)] <- sapply(carb_light_df[, c(31:33)], as.numeric)
esg_eu_df[, c(31:33)] <- sapply(esg_eu_df[, c(31:33)], as.numeric)
energy_df[, c(31:33)] <- sapply(energy_df[, c(31:33)], as.numeric)

# split the data into train/test for modeling 
set.seed(100)
heavy_split = initial_split(carb_heavy_df, prop = 0.9)
heavy_train = training(heavy_split)
heavy_test = testing(heavy_split)

light_split = initial_split(carb_light_df, prop = 0.9)
light_train = training(light_split)
light_test = testing(light_split)

energy_split = initial_split(energy_df, prop = 0.9)
energy_train = training(energy_split)
energy_test = testing(energy_split)

```


## 分析與結果

### Exploratory Data Analysis

(說明)



```{r eda, echo=FALSE, warning=FALSE, message=FALSE}

# carb emission VS. total return, correlation chart (using y~x) 
heavy.graph <- ggplot(carb_heavy_df, aes(x=CARBON_EMISSIONS_SCORE, y=TotalReturn_2y))+
  geom_point() + geom_smooth(method="lm", col="red") + ylim(-10, 1000)+ 
  ggtitle("Correlation of Emission Score to Return - Carbon Heavy Industries") + 
  labs(y = "Total Return Rate - 2 years", x = "Carbon Emission Score",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

light.graph <- ggplot(carb_light_df, aes(x=CARBON_EMISSIONS_SCORE, y=TotalReturn_2y))+
  geom_point()+ geom_smooth(method="lm", col="red") + ylim(-10, 1000)+ 
  ggtitle("Correlation of Emission Score to Return - Carbon Light Industries") + 
  labs(y = "Total Return Rate - 2 years", x = "Carbon Emission Score",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

energy.graph <- ggplot(energy_df, aes(x=CARBON_EMISSIONS_SCORE, y=TotalReturn_2y))+
  geom_point()+ geom_smooth(method="lm", col="red") + ylim(-10, 1000)+ 
  ggtitle("Correlation of Emission Score to Return - ENergy") + 
  labs(y = "Total Return Rate - 2 years", x = "Carbon Emission Score",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

# map plot - below is just to build the map
# if need to change anything, visit the below link:
# https://egallic.fr/en/european-map-using-r/

map_eu = esg_eu_df %>%
  group_by(ISSUER_CNTRY_DOMICILE) %>%
  summarise(avg_score = mean(CARBON_EMISSIONS_SCORE))

map_eu$country = c("Austria","Belgium","Germany","Denmark","Spain","Finland","France","Greece","Hungry", "Ireland","Italy","Luxembourg","Netherlands","Poland","Portugal","Sweden")

world_map <- ne_countries(scale = 50, returnclass = 'sf')
european_union <- c("Austria","Belgium","Bulgaria","Croatia","Cyprus",
                    "Czech Rep.","Denmark","Estonia","Finland","France",
                    "Germany","Greece","Hungary","Ireland","Italy","Latvia",
                    "Lithuania","Luxembourg","Malta","Netherlands","Poland",
                    "Portugal","Romania","Slovakia","Slovenia","Spain",
                    "Sweden","United Kingdom")

european_union_map <- world_map %>% 
  filter(name %in% european_union)

bbox_europe <- st_bbox(c(xmin = -10, ymin = 20, xmax = 50, ymax = 80), crs = st_crs(european_union_map))
european_union_map_cropped <- st_crop(european_union_map, bbox_europe)

map <- european_union_map_cropped %>% 
  left_join(map_eu, by = c("name" = "country"))

map.graph <- ggplot(data = map) +
  geom_sf(mapping = aes(fill = avg_score)) +
  scale_fill_gradient(name = "Carbon Emission Score", high = "#FF0000FF", low = "#FFFF00FF", na.value = "grey50")+ 
  ggtitle("Carbon Emission Score Across EU") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

showtable_df = esg_eu_df %>%
  select(TotalReturn_2y, Industry,CARBON_EMISSIONS_SCORE,IVA_COMPANY_RATING, INDUSTRY_ADJUSTED_SCORE,GOVERNANCE_PILLAR_SCORE)

# showing the data frame - important variables 
datatable(showtable_df, options = list(pageLength = 5))
```


#### 1. Correlation Plots

(說明)

```{r corr plots-1, echo=FALSE, warning=FALSE}
# showing plots
heavy.graph
```


(說明)

```{r corr plots-2, echo=FALSE, warning=FALSE}
# showing plots
light.graph
```

(說明)

```{r corr plots-3, echo=FALSE, warning=FALSE}
# showing plots
energy.graph
```

#### 2. Avergae Emission Score Across EU

(說明)

```{r map plot, echo=FALSE, warning=FALSE}
map.graph
```





### Modeling 
First, seperate data into carbon heavy industries (those 4), and carbon light industries
I used two models here, linear regression and random forest, you guys can compare the performance of both models


(說明) might want to show how you build model, what variables you included 


## Explanation (delete this after reading):
### linear regression 

To see the general view of the total return of that company, we use 2 year average total return as our outcome variable `TotalReturn_2y`, and in the RHS, we use our main focus targeted variable "carbon emission score", and other "Score" variables to control for  other related qualities of the company.

Below, we run different models on each of the industries on the train model, and then later test the model with our test set, to see which model performs better. The two models we are using are linear regression and random forest. The advantage of linear regression is that it's easier to interpret, the coeffient means the contribution of that independent variable to depedent variable. Random Forest, on the other hand might be a little difficult to the induvidual importance of the dependent variable, but it is good at finding correlation of the dependent variables by itself. So if the goal is to predict a certain company's total return based on their performance, then applying the random forest model might be a better choice.


(Hint: if you guys want to try it out, add/delete the RHS(X) variables that you might find important, and the model with the lower rmse means that model is better)

```{r all models, echo=FALSE, warning=FALSE}
#######
# linear regression 
#######
# use 2y as a try, can switch out Y variable, and/or take out "Industry"

lr_heavy = lm(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE + Industry, data = heavy_train)

lr_light = lm(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE + Industry, data = light_train, na.action=na.omit)

lr_energy = lm(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE, data = energy_train)

#######
# random forest
#######

forest_heavy = randomForest(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE + Industry, data = heavy_train, control = rpart.control(cp = 0.002, minsplit=30), importance = TRUE)

forest_light = randomForest(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE + Industry, data = light_train, control = rpart.control(cp = 0.002, minsplit=30), importance = TRUE, na.action=na.omit)

forest_energy = randomForest(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE , data = energy_train, control = rpart.control(cp = 0.002, minsplit=30), importance = TRUE, na.action=na.omit)

# predict the yhat by using the "unused" test set 
p_heavy<- predict(lr_heavy, heavy_test)
p_light<- predict(lr_light, light_test)
p_energy<- predict(lr_energy, energy_test)

# Compute errors: difference between predicted and actual test set 
error_heavy <- p_heavy - heavy_test[["TotalReturn_2y"]]
error_light <- p_light - light_test[["TotalReturn_2y"]]
error_energy <- p_energy - light_test[["TotalReturn_2y"]]

# Calculate RMSE
rmse_lm_h =sqrt(mean(error_heavy^2))
rmse_lm_l =sqrt(mean(error_light^2))
rmse_lm_e =sqrt(mean(error_energy^2))

rmse_forest_h = rmse(forest_heavy, heavy_test) 
rmse_forest_l = rmse(forest_light, light_test) 
rmse_forest_e = rmse(forest_energy, energy_test) 
```

#### Model Results {.tabset}
##### 1. Linear Model Result

(說明)


```{r model report, echo=FALSE, warning=FALSE}
# these are report of linear models
summary(lr_heavy)
summary(lr_light)
summary(lr_energy)
```
From the result above we can see that the carbon emission score is only significant in the energy industry, however, the coefficient is negative, which is not we predicted, one possible reason for that might be the energy industry is heavily depended on buring coal/gas this kind of high carbon emission activities, so that a high carbon emission score means lower productin which cause the lower 2 year total return. This hypothesis might be the same for carbon heavy industry as well, since their coefficient for carbon emission score is also negative. The coefficient for carbon emission score is only positive (as we predicted) in light carbon industry.


##### 2. Random Forest Result


(說明)

```{r model report-2, echo=FALSE, warning=FALSE}
# report of random forest model
print(forest_heavy)
print(forest_light)
print(forest_energy)

vi = varImpPlot(forest_energy, type=1, main = "Random Forest Variable Importance: Energy")

```
Although it is hard to intepret each of the coefficient in the random forest model, we can still know the importance of each varibale from this Variable Importance Plot, we can see that carbon emission score is the second most important variabes among all the "score". 

(hint: add/ delete the variable in the model building part based on how important each varible is)
##### 3. Compare Out-of-Sample Performance

(說明)
you can use `rmse_lm_h` to show the variable 


```{r rmse, echo=FALSE, warning=FALSE}
# lower RMSE means better moedle performance 
rmse_lm_h
rmse_lm_l
rmse_lm_e
rmse_forest_h
rmse_forest_l
rmse_forest_e
```
Finally we can see how the models perform based on their Root-mean-squared-error (rmse), the lower the number is, the better the model is performing. Again, each of the model has their own advantages and disadvantages, for our purpose of finding how carbon emissin score affect total return, it might be better to use rnadom forest to see which of the variables are more important then use those in linear regression to see its actual coefficent to our Y variable.


### Conclusion
(說明)
